A Linear Solution of the Linearity Challenge

### 2025-12-24 paper/Safety.lagda.tex
revised safety

We have seen that type safety is a simple instance of deadlock freedom, which is
made even simpler to formalize in our development where processes are
intrinsically typed. We start by defining reduction contexts as processes with a
single hole. In our intrinsically-typed formalization, reduction contexts are
typed and indexed by two typing contexts $\ContextD$ and $\ContextC$. The latter
is the typing context under which the reduction context as a whole is well
typed. The former is the typing context of the hole, which is invariant for a
given reduction context and therefore specified as a parameter of the data type:

@@

@@

The proof of type safety ends up being a trivial application of
\AgdaFunction{deadlock-freedom}.

>>>>

We have seen that type safety is a simple instance of deadlock freedom, which is
made even simpler to formalize in our development where processes are
intrinsically typed. We start by defining reduction contexts as processes with a
single hole. In our intrinsically-typed formalization, reduction contexts are
parameterized by the typing context $\ContextD$ of the hole, which is invariant,
and indexed by the typing context $\ContextC$ of the whole reduction context:

@@

Note the presence of two constructors \AgdaInductiveConstructor{cut-l} and
\AgdaInductiveConstructor{cut-r} which distinguish on whether the hole is found
in the left (respectively, right) sub-context, as per the grammar of reduction
contexts in \Cref{sec:properties}.

@@

The proof of type safety ends up being a trivial application of
\AgdaFunction{deadlock-freedom}, since the process $Q$ in the hole of a
reduction context is well typed by construction.
